Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-01-20 Thesis/chapter/060-results-material.tex
finish EMMA coeff analysis

%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and quite a few show hardly any current which is the ideal. 
An example for very low conductance measurement in non-logarithmic scale can be seen in figure \ref{fig:iv-nocurrent}.
For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
%
Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure \ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar}, 
but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure \ref{fig:iv-ohmic} shows a graph circa following Ohm's law. 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Preoptimization}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.

>>>>

%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and quite a few show hardly any current which is the ideal. 
An example for very low conductance measurement in non-logarithmic scale can be seen in figure \ref{fig:iv-nocurrent}.
For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
%
Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure \ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
%, but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure \ref{fig:iv-ohmic} shows a graph circa following Ohm's law. 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Preoptimization}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
The reason is that the force exerted by the blade on the liquid is not strong enough to overcome surface tension. 
This means that behind the blade a meniscus would pull the liquid without leaving behind any for the gelling process. 
Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.

### 2023-01-20 Thesis/chapter/061-results-emma.tex
finish EMMA coeff analysis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) have been investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST
The best sample predicted by the algorithm is experiment number 13 with 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature. 
lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.

\begin{table}[htb]
	\centering
    \caption{Global best per generation}
	\label{tab:emma-Gb}
	\begin{tabular}{cccccccc}
        \hline\hline
        generation  &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
        \hline
     1   &1       &2    &4   &10   &40  &120  &300\\
     2   &5       &2    &6   &10   &40  &120  &300\\
     3   &2947    &4    &6   &16   &80 &1080  &300\\
     4   &2405    &2    &6   &10   &40 &1080  &300\\
     5   &13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\end{table}

@@

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
The remaining input variables remained more or less the same except for the 3rd generation. 
%
In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}) lowered with each iteration, 
except for sample 2947, which wasn't predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
%
Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\gamma$ at the beginning and a correction with time. 
%The reason for is probably a 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements.

In figure \ref{fig:emma-gen} we can see the two measured main \textit{optimizands}, 
$\gamma$ and $\rho$, of each particle at generations 1 to 4. 
%for each particle included in the optimization. 
%It shows a clear trend which indicates that the optimization worked even though 
Both variables were to be minimized and show a clear trend towards low values, 
indicating that the optimization worked even though 
the prediction functions (see equations (\ref{eq:emma-phd3}) - (\ref{eq:emma-vcal4})) 
and the chosen samples where not exactly as expected. 
Neither were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables like room temperature or humidity.

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process} 
    \label{fig:emma-gen}
\end{figure}

%%% EQUATION 
%\subsubsection{Equation}
Equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})-(\ref{eq:emma-vcal4}) represent the \gls{rf}s at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
%$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
and $h(6-\lambda)$ into layer count influential only if under 6.
%
The first thing to notice is that prediction functions of each generation depend on the same variables. 
%This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
This stems from the fact that the algorithm choses a single minimal set of \gls{bf} to predict all dependent variables. 
%
%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
%As the \gls{mars} algorithm is greedy,
%Different independent variables compete to be used as \gls{bf} in the prediction functions because of the greediness of the \gls{mars} algorithm. 
%}

@@

The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
This fits the data well, but the positive influence of the layer count $\lambda$ is counter intuitive 
as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
seem low, but - considering the minimum value of the interaction of \num{36000} - have a higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term. 
%It's positive the hinge
It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) was chosen so low; 
basically only including the influence of $\lambda=4$.
Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
On the positive side, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
The choice of \gls{bf}s in combination with their coefficient signs seems more plausibel
for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally the lowest $\lambda$ increases the two \textit{optimizands}. 
Highly interesting is the influence of $T_{cal}$ on the measure of conductance of a sample. 
The optimzand $\hat{\gamma}$ increases with higher calcination temperature, 
ergo the resistance decreases contrary to expectations.
It was expected that 
%under \oc{400} the calcination does not fully \td{ablaufen} and 
calcination under \oc{400} does not suffice and 
that therefore the resulting layer does not insulate as well. 
Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$.
%This becomes clear when looking at the data.
The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size, 
but has the extra factor of $\lambda$ of up to 12, resulting in the products being in the same order of magnitude.
It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
This could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
%It should be doubted, though, that the $layr$ only appears as interaction term 
%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
with $T_{cal}$ and $T_{DB}$.

@@

%%% PROBLEMS 
Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency of chosen dependent varibales. 
This is mainly because of the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
In the here presented optimisation model the data points per independent variable 
(events per predictor variable EPV) are as low as 5. 
By eliminating three independent variables the EVP could rise to 10, which is stated 
as rule of tumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver some insightfulness %are quite respectable. 
considering an EPV of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an EVP of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the EVP is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%
The main problem about too many independent variables specific to this optimisation procedure 
is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
This effect is reinforced by the choice of two independent variables as dependent variables. % (IVDV). 
Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
for including them in the \gls{rf}s is an easy way to reduce the \gls{mse}.
These \gls{bf}s then "take away places" of \gls{bf}s predicting other dependent variables in the \gls{rf}. %\td{(cf. musical chairs)} 
This in turn can lead to wrong predictions and therefore inefficient choice of future samples.

\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
\td{look at emma papers}
\td{change G to gamma and write enr to every figure}
\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
EPV is around 5 for this model.
Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) have been investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST PREDICTED RECIPE
The best sample predicted by the algorithm is experiment number 13 with 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature. 
lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.

\begin{table}[htb]
	\centering
    \caption{Global best per generation}
	\label{tab:emma-Gb}
	\begin{tabular}{ccccccccc}
        \hline\hline
		generation& measurements &enr &$c_{zr}$ &$\lambda$ &$v_{DB}$ &$T_{DB}$ &$v_{cal}$ &$T_{cal}$\\
        \hline
	1  &10	&1       &2    &4   &10   &40  &120  &300\\
	2  &15	&5       &2    &6   &10   &40  &120  &300\\
	3  &20	&2947    &4    &6   &16   &80 &1080  &300\\
	4  &25	&2405    &2    &6   &10   &40 &1080  &300\\
	5  &30	&13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\end{table}

@@

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
The remaining input variables remained more or less the same except for the 3rd generation. 
\td{why?}
%
In table \ref{tab:emma-pred-G} it can be seen that the predicted $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
except for sample 2947, which wasn't predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
%
Contrarily, the predicted $\hat{\gamma}$ for each generation's best 
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
%The reason for is probably a 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
Indeed, the samples with the lowest \textit{optimisands} are amoung the first generation (see appendix \ref{sec:app-emma}, \td{and maybe fig gen-g}).

In figure \ref{fig:emma-gen} we can see the two measured main \textit{optimisands}, 
$\gamma$ and $\rho$, of each particle at generations 1 to 4. 
%for each particle included in the optimization. 
%It shows a clear trend which indicates that the optimization worked even though 
Both variables were to be minimized and show a clear trend towards low values with increasing generation, 
indicating that the optimization worked even though 
the prediction functions (see equations (\ref{eq:emma-phd3}) - (\ref{eq:emma-vcal4})) 
and the chosen samples where not exactly as expected. 
Neither were the measurements for these samples, which might be due to the high measuring error of samples and variation of quality due to uncontrolled independent variables like room temperature or humidity.

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process; \td{add caption for c and d. check if can plot with t=0}} 
    \label{fig:emma-gen}
\end{figure}

%%% EQUATION 
%\subsubsection{Equation}
Equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) and (\ref{eq:emma-phd4})-(\ref{eq:emma-vcal4}) represent the \gls{rf}s at $t=3$ and $t=4$, respsectively, rounded to 2 significant digits.
%$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
and $h(6-\lambda)$ into layer count influential only if under 6.
%
The first thing to notice is that prediction functions of each generation depend on the same variables. 
%This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
This stems from the fact that the algorithm choses a single minimal set of \gls{bf} to predict all dependent variables. 
%
%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimisands} rather unfortunate. %highly questionable. 
%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
%As the \gls{mars} algorithm is greedy,
%Different independent variables compete to be used as \gls{bf} in the prediction functions because of the greediness of the \gls{mars} algorithm. 
%}

@@

The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
This fits the data well (see appendix \ref{sec:app-emma}), but the positive influence of the layer count $\lambda$ is counter intuitive 
as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
seem low, but - considering the minimum value of the interaction of \num{36000} - have a higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term. 
%It's positive the hinge
It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})-(\ref{eq:emma-vcal3}) was chosen so low; 
basically only including the influence of $\lambda=4$.
Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
On the positive side, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
The choice of \gls{bf}s in combination with their coefficient signs seems more plausibel
for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally the lowest $\lambda$ increases the two \textit{optimisands}. 
% TCAL ON OPTIMIZANDS
The influence of $T_{cal}$ on the measures of conductance ($\rho$ and $\gamma$) is higly interesting. 
It was expected that 
calcination temperatures under \oc{400} do not suffice to produce compact layers and 
that therefore the resulting layer does not insulate as well. 
%\td{xxx}
\textit{Optimsands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
according to equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}, 
ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
% DESCRIBE COEFFEICIENTS
Furthermore, the influence of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$ and also on $\hat\lambda$ and $\hat{v}_{cal}$.
The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
but has the extra factor $\lambda$ of up to 12, resulting in the products of coefficients and independent variable being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
This negative correlation could hint a compensation of the overestimated influence of $T_{cal}$ on the \textit{optimisands}.
%It should be doubted, though, that the $layr$ only appears as interaction term 
%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
%
%It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
%with $T_{cal}$ and $T_{DB}$. 
From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_DB$ and then the rest of the independent variables. 
I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.

@@

\td{plot g and p vs TCal, calc avg of p and g for each gen, append pre-emma to appendix}
%%% PROBLEMS 
Even though the main \textit{optimisands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency of chosen dependent varibales. 
This is mainly because of the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
In the here presented optimisation model the data points per independent variable 
(events per predictor variable EPV) are as low as 5. 
By eliminating three independent variables the EVP could rise to 10, which is stated 
as rule of tumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver some insightfulness %are quite respectable. 
considering an EPV of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an EVP of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the EVP is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%
The main problem about too many independent variables specific to this optimisation procedure 
is that the same set of \gls{bf}s will be used to predict all \textit{optimisands}.
This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
This effect is reinforced by the choice of two independent variables as dependent variables. % (IVDV). 
Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
for including them in the \gls{rf}s is an easy way to reduce the \gls{mse}.
These \gls{bf}s then "take away places" of \gls{bf}s predicting other dependent variables in the \gls{rf}. %\td{(cf. musical chairs)} 
This in turn can lead to wrong predictions and therefore inefficient choice of future samples.

\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
\td{look at emma papers}
\td{change G to gamma and write enr to every figure}
\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
EPV is around 5 for this model.
Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
}
